Tidal field anisotropy as a tracer of cosmic voids

### 2015-01-10 cosmic_voids.tex
Section 5.1, Enclosed mass, done

This paper is organized as follows. 
In Section \ref{sec:algorithms_cosmic_web} we describe the algorithms
we use to find the cosmic web in N-body simulations. 
Then in Section \ref{sec:bulk_voids} we explain in detail our void
finder based on the fractional anisotropy of the tidal and shear
tensor fields. 
In Section \ref{sec:experiments} we describe the numerical experiments
we perform to show the performance of the new void finding technique.  
Our results are presented in \ref{sec:results} to finally comment and
conclude about these findings in Section \ref{sec:conclusions}.

@@

\section{Numerical Simulations}
\label{sec:simulatins}

@@

\subsection{Defining voids with a watershed algorithm}
\label{sec:watershed}

@@

@@

%-------------------------------------------------------------------------
\subsection{Density profile of voids}
\label{subsec:density_voids}
%-------------------------------------------------------------------------

\[ \mathcal{C} = \frac{M_v}{\overline{M}} = \frac{3}{2R^{3}} \int_0^{R} [\delta(r) + 1] r^2 dr \]

\[ \mathcal{C} < 1 \]

\[ \mathcal{C} > 1 \]

@@

%.........................................................................
%FIGURE 3: FA of some regions and shape illustration
%\begin{flushleft}
%\begin{figure*}
%\centering
%  \includegraphics[trim = 0mm 1mm 0mm 1mm, clip, keepaspectratio=true,
%  width=0.3\textheight]{./figures/FA_Prolatenes_Vweb.pdf}
%  \includegraphics[trim = 0mm 1mm 0mm 1mm, clip, keepaspectratio=true,
%  width=0.3\textheight]{./figures/FA_Prolatenes.png}

@@

%.........................................................................
%FIGURE 4: volume functions
\begin{flushleft}
\begin{figure*}
\centering

  \captionof{figure}{\small Volume functions of voids for both built 
  catalogs. Watershed-Tweb (red curves), Watershed-Vweb (blue curves).
  Continuous lines corresponds with the total number of voids, dot-dashed
  with sub-compensated voids and dashed lines with over-compensated voids. }

%.........................................................................
%FIGURE 5: Density profile of voids for each defined scheme
\begin{flushleft}
\begin{figure*}
\centering
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_density_TwebFAG0.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_velocity_TwebFAG0.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_FA_TwebFAG0.pdf}

>>>>

This paper is organized as follows. 
In Section \ref{sec:algorithms_cosmic_web} we describe the algorithms
we use to find the cosmic web in N-body simulations. In Section 
\ref{sec:simulations} we describe the used simulation.
Then in Section \ref{sec:bulk_voids} we explain in detail our void
finder based on the fractional anisotropy of the tidal and shear
tensor fields.
%In Section \ref{sec:experiments} we describe the numerical experiments
%we perform to show the performance of the new void finding technique.
Our results are presented in \ref{sec:results} to finally comment and
conclude about these findings in Section \ref{sec:conclusions}.

@@

\section{Numerical Simulations}
\label{sec:simulations}

@@

%-------------------------------------------------------------------------
\subsection{Defining voids with a watershed algorithm}
\label{sec:watershed}
%-------------------------------------------------------------------------

@@

%-------------------------------------------------------------------------
\subsection{Enclosed mass}
\label{subsec:enclosedmass}
%-------------------------------------------------------------------------thereby allowing a good classification criterion

When we analyse individual density profiles of voids (see left panels of
Fig. \ref{fig:RhoVel}), they seem to be distributed in two different 
families, differentiated by the presence or absence or a compensation 
ridge (e.g. see also Fig. 14 of \citet{Colberg05}). In order to discriminate 
each void in one of the families, we propose the compensation index, which 
is defined as the mass of a void enclosed at a spherical volume of radius $R$ 
and normalized by the mass of the same volume as assuming the mean background
density instead

\eq{compensation}
{\mathcal{C} = \frac{M_v}{\overline{M}} = \frac{3}{2R^{3}} \int_0^{R} [\delta(r) + 1] r^2 dr}

We choose an integration radius of $R=4r_{eff}$, which is large enough to 
enclose the compensation ridge for a typical void in case there is one. 
This leads us to voids with $\mathcal{C}>1$ have more mass than expected, 
constituting the family of overcompensated voids. These voids generally 
exhibit a compensation ridge. In the same fashion, voids with 
$\mathcal{C}<1$ constitute the family of subcompensated voids.

@@

%.........................................................................
%FIGURE 3: volume functions
\begin{flushleft}
\begin{figure}
\centering

  \captionof{figure}{\small Volume size distribution of voids for both
  catalogs. FA-Tweb (red curves), FA-Vweb (blue curves).
  Continuous lines corresponds with the total number of voids, dot-dashed
  with sub-compensated voids and dashed lines with over-compensated voids. }

\end{figure}
\end{flushleft}
%.........................................................................

%-------------------------------------------------------------------------
\subsection{Physical profiles of voids}
\label{subsec:density_voids}
%-------------------------------------------------------------------------

@@

%.........................................................................
%FIGURE -: FA of some regions and shape illustration
%\begin{flushleft}
%\begin{figure*}
%\centering
%  \includegraphics[trim = 0mm 1mm 0mm 1mm, clip, keepaspectratio=true,
%  width=0.3\textheight]{./figures/FA_Prolatenes_Vweb.pdf}
%  \includegraphics[trim = 0mm 1mm 0mm 1mm, clip, keepaspectratio=true,
%  width=0.3\textheight]{./figures/FA_Prolatenes.png}

@@

%.........................................................................
%FIGURE 4: Density profile of voids for each defined scheme
\begin{flushleft}
\begin{figure*}
\centering
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_density_TwebFAG0.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_velocity_TwebFAG0.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_FA_TwebFAG0.pdf}
